---
title: "Homework 24"
format: html
editor: visual
---

## Overview

For your homework you will implement a data analysis using a dataset on crab growth measurements.

Set things up (hint: there is a new package to add with `library()`)

```{r}
rm(list=ls())
library(tidyverse)
library(here)
library(ggfortify)
```

## The data

Let's pull in some data appropriate biologists: crab measurements. This dataset includes measurements of farmed crabs.

```{r}
crabs <- read.csv(here("data", "CrabAgePrediction.csv"))
glimpse(crabs)
```

One of the variables is categorical - let's fix that in the data.

```{r}
crabs$Sex <- as.factor(crabs$Sex)
```

## Question

Is there a relationship between height and weight in female crabs?

1.  Extract the data for just female crabs.

    ```{r}
   female <-  crabs %>% group_by(Sex) %>% 
      filter(Sex == 'F')

    ```

2.  Examine the response and predictor variables and use the flow chart from class to decide the appropriate statistical analysis (choose from: chi-square, 2-sample t-test or linear regression). Explain your answer here:
```{r}
model_hw <- lm(Height ~ Weight, data = female)
autoplot(model_hw, smooth.colour = NA)
```

3.  Work through the data analysis **following all of the steps provided in chapter 5 of your book**. You may use class notes or homework keys as a guide.
```{r}
anova(model_hw)
summary(model_hw)
ggplot(female, aes( x= Weight, y= Height)) + geom_point() + geom_smooth(method = 'lm')
```

## 
